ABX usage

### 2019-12-13 scripts/29_abx_usage.Rmd
update

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r}

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(lubridate)
```

```{r}
# the current shotgun data
sg <- read_csv('../data/cleaned_pheno/final_pheno.csv')

# the updated baseline sample collection date
bcd <- read_csv('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/SampleDates12-12-2019.csv', 
                col_types = cols(.default = col_character())) %>% 
  mutate(datecollection = mdy(datecollection)) %>% 
  filter(str_detect(window, 'Baseline')) %>% 
  filter(sampleid %in% sg$sampleid)

# load the updated abx usage table
abx <- read_csv('../data/cleaned_pheno/copy12_12_abx.csv', col_types = cols(.default = col_character())) %>% 
  filter(MRN %in% bcd$mrn) %>% 
  dplyr::select(MRN, 
                Antibiotics, 
                start = `Start date`,
                end = `End Dates`) %>% 
  # there is one patient has None abx
  filter(!is.na(start)) %>% 
  mutate(start = mdy(start),
         end = mdy(end)) %>% 
  # join in the date of baseline sample collection
  left_join(bcd %>% 
              dplyr::select(mrn, datecollection), by = c('MRN'='mrn')) %>% 
  mutate(startday = start - datecollection,
         endday = end - datecollection)
```

```{r}
# create a table that has Y and N for abx usage 4 weeks prior to the baseline sample collection date
fil <- abx %>% 
  filter(startday <= 0 ) %>% 
  distinct(MRN)
